---
title: "Project 1 - Question 1"
output:
  html_document: default
  pdf_document: default
  author: Maryam Imani, Azadeh Samadian
---

# Reading data from the file 

```{r , echo=TRUE}
mydata <- read.table("token/networkomisegoTX.txt", header=FALSE, 
  	sep=" ",  col.names= c("fromNodeID", "toNodeID", "unixTime", "tokenAmount"), colClasses=c('factor', 'factor', 'numeric', 'numeric') )
summary(mydata)
```
# Outlier

```{r , echo=TRUE}
maxTotalSupply<-140245398
subUnit<-10^18
outlier_value <- maxTotalSupply*subUnit
outlierData <- mydata [which(mydata$tokenAmount > outlier_value),]
#head(outlierData)
#library("dplyr")
#filter(mydata, tokenAmount < outlier_value)
message("Total Number of Outliers: ", length(outlierData$tokenAmount))
```

## Number of users that included in outliers transactions: 
```{r , echo=TRUE}
users <- c(outlierData$fromNodeID, outlierData$toNodeID)
uniqueUsers <- unique(users)
message(length(uniqueUsers), " users are included in outliers transactions.")
```
## Remove outliers:
```{r , echo=TRUE}
withoutOutlierData <- mydata [which(mydata$tokenAmount < outlier_value),]

```

# Finding the frequency of each seller 

```{r , echo=TRUE}
w <- table(withoutOutlierData$fromNodeID)
Seller <- as.data.frame(w)
names(Seller)[1] <- 'Seller'
head(Seller)
```
# Finding the frequncy of frequency of sellers
```{r, echo=TRUE}
w2 <- table(Seller$Freq)
FreqSeller <-as.data.frame(w2)
colnames(FreqSeller) <- c("NumSeller", "FreqNumSeller")
head(FreqSeller)
barplot(FreqSeller$FreqNumSeller, names.arg = FreqSeller$NumSeller, ylab = "frequency of Number of Seller", xlab="Frequency", xlim = c(0, 50))
```

```{r, echo= TRUE}

library(fitdistrplus)
library(logspline)

descdist(FreqSeller$FreqNumSeller, discrete = FALSE)
```
```{r, echo=TRUE}
plotdist(FreqSeller$FreqNumSeller, histo = TRUE, demp = TRUE)

```
### Testing Normal Distribution 
```{r, echo = TRUE}
fit.norm <- fitdist(FreqSeller$FreqNumSeller, "norm")
plot(fit.norm)
fit.norm
```
### Testing Log-Normal Distribution 
```{r, echo = TRUE}
fit.lnorm <- fitdist(FreqSeller$FreqNumSeller, "lnorm")
plot(fit.lnorm)
fit.lnorm
```
### Testing Poisson distribution 
```{r, echo= TRUE}
fit.pois <- fitdist(FreqSeller$FreqNumSeller, "pois", method = "mle")
plot(fit.pois)
fit.pois
```
### Testing Negative Binomial Distribution 
```{r, echo= TRUE}
fit.nb <- fitdist(FreqSeller$FreqNumSeller, "nbinom")
plot(fit.nb)
fit.nb
```
### Testing Weibull distribution 
```{r, echo= TRUE}
fit.weibull <- fitdist(FreqSeller$FreqNumSeller, "weibull")
plot(fit.weibull)
fit.weibull
```
### Testing Exponential Distribution 
```{r, echo= TRUE}
fit.exp <- fitdist(FreqSeller$FreqNumSeller, "exp", method="mme")
plot(fit.exp)
fit.exp
```
### Comparision between different disribtions 
```{r, echo= TRUE}
par(mfrow=c(2,2))
plot.legend <- c("Weibull", "lognormal", "poisson", "Exponential")
denscomp(list(fit.weibull, fit.lnorm, fit.pois, fit.exp), legendtext = plot.legend)
cdfcomp (list(fit.weibull, fit.lnorm, fit.pois, fit.exp), legendtext = plot.legend)
qqcomp  (list(fit.weibull, fit.lnorm, fit.pois, fit.exp), legendtext = plot.legend)
ppcomp  (list(fit.weibull, fit.lnorm, fit.pois, fit.exp), legendtext = plot.legend)
```

# Finding the frequency of each buyer 

```{r , echo=TRUE}
w <- table(withoutOutlierData$toNodeID)
Buyer <- as.data.frame(w)
names(Buyer)[1] <- 'Buyer'
head(Buyer)
```
# Finding the frequncy of frequency of buyers
```{r, echo=TRUE}
w2 <- table(Buyer$Freq)
FreqBuyer <-as.data.frame(w2)
colnames(FreqBuyer) <- c("NumBuyer", "FreqNumBuyer")
head(FreqBuyer)
barplot(FreqBuyer$FreqNumBuyer, names.arg = FreqBuyer$NumBuyer, ylab = "frequency of Number of Buyer", xlab="Frequency", xlim = c(0, 50))
```

```{r, echo= TRUE}
library(fitdistrplus)
library(logspline)

descdist(FreqBuyer$FreqNumBuyer, discrete = FALSE)
```
```{r, echo=TRUE}
plotdist(FreqBuyer$FreqNumBuyer, histo = TRUE, demp = TRUE)

```
### Testing Normal Distribution 
```{r, echo = TRUE}
fit.norm <- fitdist(FreqBuyer$FreqNumBuyer, "norm")
plot(fit.norm)
fit.norm
```
### Testing Log-Normal Distribution 
```{r, echo = TRUE}
fit.lnorm <- fitdist(FreqBuyer$FreqNumBuyer, "lnorm")
plot(fit.lnorm)
fit.lnorm
```

### Testing Poisson Distribution 
```{r, echo= TRUE}
fit.pois <- fitdist(FreqBuyer$FreqNumBuyer, "pois", method = "mle")
plot(fit.pois)
fit.pois
```
### Testing Negative Binomial Distribution
```{r, echo= TRUE}
fit.nb <- fitdist(FreqBuyer$FreqNumBuyer, "nbinom")
plot(fit.nb)
fit.nb
```
### Testing Weibull Distribution 
```{r, echo= TRUE}
fit.weibull <- fitdist(FreqBuyer$FreqNumBuyer, "weibull")
plot(fit.weibull)
fit.weibull
```
### Testing exp Distribution 
```{r, echo= TRUE}
fit.exp <- fitdist(FreqBuyer$FreqNumBuyer, "exp", method="mme")
plot(fit.exp)
fit.exp
```

### Comparision between different disribtions 
```{r, echo= TRUE}
par(mfrow=c(2,2))
plot.legend <- c("Weibull", "lognormal", "poisson", "exponential")
denscomp(list(fit.weibull, fit.lnorm, fit.pois, fit.exp), legendtext = plot.legend)
cdfcomp (list(fit.weibull, fit.lnorm, fit.pois, fit.exp), legendtext = plot.legend)
qqcomp  (list(fit.weibull, fit.lnorm, fit.pois, fit.exp), legendtext = plot.legend)
ppcomp  (list(fit.weibull, fit.lnorm, fit.pois, fit.exp), legendtext = plot.legend)
```

We guess both of buyers and sellers frequency can fit with Exponential distributions. 
